---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# cblindplot

<!-- badges: start -->
[![main](https://github.com/ducciorocchini/cblindplot/actions/workflows/main.yaml/badge.svg)](https://github.com/ducciorocchini/cblindplot/actions/workflows/main.yaml)
<!-- badges: end -->

**cblindplot** R package is described in Rocchini et al. - https://doi.org/10.1016/j.ecoinf.2023.102045.

## Installation

You can install the development version of **cblindplot** from [GitHub](https://github.com/) with:

``` r
# install.packages("remotes")
remotes::install_github("ducciorocchini/cblindplot")
```

## Example

```{r example}
library(cblindplot)
my_image <- system.file("pic/imager.png", package = "cblindplot")
```

```{r}
#| warning: false
my_image_terra <- terra::rast(my_image)
terra::plotRGB(my_image_terra)
```

```{r}
cblind.plot(my_image, cvd = "deuteranopia")
```

## Citation

To cite the **cblindplot** package in publications, please use [this paper](https://doi.org/10.1016/j.ecoinf.2023.102045):

> Rocchini, D., Nowosad, J., D’Introno, R., Chieffallo, L., Bacaro, G., Gatti, R. C., Foody, G. M., Furrer, R., Gabor, L., Malavasi, M., Marcantonio, M., Marchetto, E., Moudry, V., Ricotta, C., Simova, P., Torresani, M., & Thouverai, E. (2023). Scientific maps should reach everyone: The cblindplot R package to let colour blind people visualise spatial patterns. Ecological Informatics. https://doi.org/10.1016/j.ecoinf.2023.102045

LaTeX/BibTeX version can be obtained with:

```
library(cblindplot)
citation("cblindplot")
```
